\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
Paper v2
FIXED?

We began our research by looking for current satellite encryption. We found a paper on AES (Advanced Encryption Standard) with LDPC (Low Density Parity Check Code) in order to design a secure and reliable error correction method. \cite{SEEC} We also found that stream ciphers lead to serious problems if used incorrectly for satellite applications. \cite{stream_problems} We discovered someone else's work to authenticate IP protocol. \cite{IP_Protocol} In order to meet the low overhead requirement we found a low cost one-way HMAC proposal for a RFID system. \cite{HMAC_RFID} With all of this information, we needed a light weight software library for encryption to use. 

@@

The LiteCrypto library is available at https://github.com/WardenGnaw/LiteCrypto. It is available for anyone to use and modify. After further testing with CubeSat, LiteCrypto will hopefully be integrated for use.

>>>>

We began our research by looking for current satellite encryption. We found a paper on AES (Advanced Encryption Standard) with LDPC (Low Density Parity Check Code) in order to design a secure and reliable error correction method. \cite{SEEC} We also found that stream ciphers lead to serious problems if used incorrectly for satellite applications. \cite{streamproblems} We discovered someone else's work to authenticate IP protocol. \cite{IPProtocol} In order to meet the low overhead requirement we found a low cost one-way HMAC proposal for a RFID system. \cite{HMACRFID} With all of this information, we needed a light weight software library for encryption to use. 

@@

The LiteCrypto library is available at \url{https://github.com/WardenGnaw/LiteCrypto}. It is available for anyone to use and modify. After further testing with CubeSat, LiteCrypto will hopefully be integrated for use.
